---
title: "Introduction to ggplot2"
author: "Manuel Gijón Agudo"
date: '`r format(Sys.Date(),"%e de %B, %Y")`'
output:
  pdf_document:
    toc: yes
    toc_depth: 2
  html_document:
    toc: yes
    toc_depth: 2
    toc_float: yes
lang: en # language,  en: english (default), es: espa?ol, ca: catalan, ...
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

-----------------------

This is just an introduction to the syntax an idiosyncrasy of ggplot2 package. We are going to use a simple scatterplot and a preload dataset.

-----------------------


# First steps

The first step is to load the library or install it if it si not.

```{r instalation, echo=TRUE}
#install.packages("ggplot")  # uncommented in case it is not installed
library(ggplot2)
```

First we are going to initialize based on a preloaded dataset.

```{r first-steps, echo=TRUE}
# Setup
options(scipen=999)  # turn off scientific notation like 1e+06
data("midwest", package = "ggplot2")  # load the data

# Init ggplot
ggplot(midwest, aes(x = area, y = poptotal))  # area and poptotal are columns in 'midwest'```
```

**Note** that we are using the function ```aes``` to specify the axis to ggplot.

# Simple scatterplot

We'll use the function ```geom_point()``` to add the points to the canvas.

```{r simple_scaterplot, echo=FALSE}
ggplot(midwest, aes(x = area, y = poptotal)) + geom_point()
```

Now we are saving the graphic like an object in the envairoment of variables in R. We call it ```g```, so to plot it we need to use the function ```plot``` aplied to the object.
```{r, echo=TRUE}
g <- ggplot(midwest, aes(x = area, y = poptotal)) + geom_point() + geom_smooth(method = "lm")  
plot(g)
```

**Note**: the function ```geom_smooth``` is used here with the paramether and the values ```method = "lm"``` to plot a linear regresion that includes the confidence intervals.


## Adjusting axis

### Deleting points outside the range

In this case we delete the point by fixing a range, the points outside will be remove.
```{r deletingPoints, echo=TRUE}
g <- ggplot(midwest, aes(x = area, y = poptotal)) + geom_point() + geom_smooth(method = "lm", se=FALSE)  

# Delete the points outside the limits
g + xlim(c(0, 0.1)) + ylim(c(0, 500000))   # deletes points
```

**Notes**: 
  * Be aware that the paramether ```se``` with the value ```FALSE``` erase the confidence interval. Realise also that the default value is ```TRUE```.
  * See that changing the total amount of points the regresion line change too.

### Zooming in

```{r zoomingIn, echo=TRUE}
g <- ggplot(midwest, aes(x = area, y = poptotal)) + geom_point() + geom_smooth(method = "lm")  

g1 <- g + coord_cartesian(xlim = c(0,0.1), ylim = c(0, 1000000))  
plot(g1)
```


## Changing titles and labels

This section consists just in present by an example the paramethers of the function to manipulate.
```{r titles, echo=TRUE}
ggplot(midwest, aes(x = area, y = poptotal)) + 
      geom_point() + 
      geom_smooth(method = "lm") + 
      coord_cartesian(xlim = c(0,0.1), ylim = c(0, 1000000)) + 
      labs(title = "Area Vs Population", 
           subtitle = "From midwest dataset",
           y = "Population", 
           x = "Area",
           caption = "Midwest Demographics")
```

## Color and size of the points

### Static

In this case we specify the color.

```{r colors-sizes, echo=TRUE}
ggplot(midwest, aes(x = area, y = poptotal)) + 
      geom_point(col = "steelblue", size = 3) +   # Set static color and size for points
      geom_smooth(method = "lm", col = "firebrick") +  # change the color of line
      coord_cartesian(xlim = c(0, 0.1), ylim = c(0, 1000000)) + 
      labs(title = "Area Vs Population", 
           subtitle = "From midwest dataset", 
           y = "Population", 
           x = "Area", 
           caption = "Midwest Demographics")
```

### Categories

We specify a category of colors, ie. a collection of colors.

```{r colors_categories, echo=TRUE}
gg <- ggplot(midwest, aes(x = area, y = poptotal)) + 
            geom_point(aes(col = state), size = 3) +  # Set color to vary based on state categories.
            geom_smooth(method = "lm", col = "firebrick", size = 2) + 
            coord_cartesian(xlim = c(0, 0.1), ylim = c(0, 1000000)) + 
            labs(title = "Area Vs Population", 
                 subtitle = "From midwest dataset",
                 y = "Population", 
                 x = "Area", caption = "Midwest Demographics")
plot(gg)
```


#### Another paletes of color

With this package we would have more palets to use.

```{r palette, echo=TRUE}
#trinstall.packages("RColorBrewer")    # uncommented in case it is not installed
library(RColorBrewer)
head(brewer.pal.info, 10)  
```

**Note**: see that the ```head```function is just to show us the first (```10``` in this case) elements in a collections of elements saved in a data.frame object.

## Change the X axis texts and ticks location

* *Step 1*: Set the breaks

```{r step1, echo=TRUE}
# Base plot
gg <- ggplot(midwest, aes(x = area, y = poptotal)) + 
            geom_point(aes(col = state), size = 3) +  # Set color to vary based on state categories.
            geom_smooth(method = "lm", col = "firebrick", size = 2) + 
            coord_cartesian(xlim = c(0, 0.1), ylim = c(0, 1000000)) + 
            labs(title = "Area Vs Population",
                 subtitle = "From midwest dataset", 
                 y = "Population", 
                 x = "Area", 
                 caption = "Midwest Demographics")

# Change breaks
gg + scale_x_continuous(breaks = seq(0, 0.1, 0.01))
```

**Note**: the function ```breaks``` create an array with numbers from 0 to 0.1 whit a step size of 0.01.

* *Step 2*: Change the labels
```{r step2, echo=TRUE}
gg + scale_x_continuous(breaks = seq(0, 0.1, 0.01), labels = letters[1:11])
```


**Note**: we can reverse the edges using the next function.

```{r reverse, echo=TRUE}
# Reverse X Axis Scale
gg + scale_x_reverse()
```








**Source**: http://r-statistics.co/Complete-Ggplot2-Tutorial-Part1-With-R-Code.html



