---
title: "Tutorial: ggmap"
author: "Manuel Gijón Agudo"
date: "12 de julio de 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GGMAP

This package has the same structure and philosophy than ggplot but for georeferencial information.

First load the package in your script or markdown.

```{r cars}
#install.packages('ggmap')    # uncomented to intall the library if need it
library(ggmap)
```

### First steeps


```{r pressure, echo=FALSE}
qmap(location = "barcelona")
```

Zoom = 10 as the default value.
```{r pressure, echo=FALSE}
qmap(location = "barcelona", zoom = 15)
```

```{r pressure, echo=FALSE}
qmap(location = "barcelona", maptype = "satellite")
```

```{r pressure, echo=FALSE}
qmap(location = "barcelona", maptype = "hybrid")
```

```{r pressure, echo=FALSE}
qmap(location = "barcelona", maptype = "toner")
```

```{r pressure, echo=FALSE}
qmap(location = "barcelona",  maptype = "watercolor")
```

```{r pressure, echo=FALSE}
qmap(location = "barcelona", maptype = "terrain-background")
```


```{r pressure, echo=FALSE}
qmap(location = "barcelona", maptype = "toner-lite")
```

get_map(location = c(lon = -95.3632715, lat = 29.7632836), zoom = "auto", scale = "auto", maptype = c("terrain", "terrain-background", "satellite", "roadmap", "hybrid", "toner", "watercolor", "terrain-labels", "terrain-lines", "toner-2010", "toner-2011", "toner-background", "toner-hybrid", "toner-labels", "toner-lines", "toner-lite"), source = c("google", "osm", "stamen", "cloudmade"), force = ifelse(source == "google", TRUE, TRUE), messaging = FALSE, urlonly = FALSE, filename = "ggmapTemp", crop = TRUE, color = c("color", "bw"), language = "en-EN", api_key)
```{r pressure, echo=FALSE}
map <- get_map()
map
str(map)
ggmap(map)
```

```{r pressure, echo=FALSE}
map <- get_map(location = "Barcelona", zoom = 6, source = "google")
ggmap(map, fullpage = TRUE)
```